Calculate FD

### 2020-08-31 analysis/calc_fd.Rmd
Cap number of PCA axes and use Cailliez rather than square root correction.

```{r}
library(tidyverse)
library(furrr)
library(FD)
library(biodivTS)
```

@@

get_fd <- function(obs_data, filter_plot){
  require(FD)

@@

  species_mat <- data %>%
    select(year, id, sum_abundance) %>% 
    distinct() %>%
    arrange(year, id) %>%
    spread(id, value = sum_abundance, fill = 0) %>%
    select(-year)

@@

  fd_out <- as_tibble(dbFD_joggle(trait_mat, species_mat, w.abun = FALSE))[,1:8] %>%
    cbind(years, .) %>%
    mutate(plot_id = unlist(filter_plot), trait_count = dim(trait_mat)[2])
    write_tsv(fd_out, paste0(here::here("data"), "/fd_output/", filter_plot, "_fd.tsv"))

@@

First pass at calculating FD metrics from FD package:
```{r}
data <- biotime_traits %>% 
  filter(!is.na(plot)) %>% #remove unlabeled plots 
  group_by(plot_id, year) %>%
  filter(n_distinct(id) > 4) %>%
  group_by(plot_id) %>%
  filter(n_distinct(year) > 4) %>% 
  ungroup() #%>%
  #filter(#!study_id %in% c(195, 360), #exclude because they break
         #!study_id %in% c(217, 327, 195)) #exclude to get the file size smaller

plots <- data %>%
  pull(plot_id) %>%
  unique()

#system.time(fd <- future_map(plots[1:3], get_fd_safe, obs_data = data))
```

@@

attempted <- dir(here::here("data", "fd_attempt"), "*.tsv") %>%
  str_replace(".tsv", "") %>%
  as.numeric()

remain <- data %>%
  filter(!plot_id %in% fd_data$plot_id, 
         !plot_id %in% attempted,
         !plot_id %in% c(1661, 196456, 3721, 3601, 2171))#1952507

plot_sizes <- remain %>%
  count(plot_id) %>%
  arrange(desc(n)) %>%
  mutate(group = rep_len(1:num_groups, dim(.)[1]))

#fd <- map(1:num_groups, get_parallel_FD, df = remain)

system.time(fd <- map(plot_sizes$plot_id, get_fd_safe, obs_data = data))
```

@@

usethis::use_data(fd_table)
```

>>>>

```{r}
library(tidyverse)
library(furrr)
library(FD)
library(biodivTS)

pins::board_register_github(repo = "karinorman/biodivTS", branch = "master")
```

@@

get_fd <- function(obs_data, filter_plot, ...){
  require(FD)

@@

  species_mat <- data %>%
    group_by(year, id) %>%
    summarise(abun = sum(sum_abundance)) %>%
    ungroup() %>%
    arrange(year) %>%
    arrange(id) %>%
    pivot_wider(names_from = id, values_from = abun, values_fill = 0) %>%
    select(-year)

@@

  fd_out <- as_tibble(dbFD_joggle(trait_mat, species_mat, w.abun = TRUE, m = "min", ...))[,1:8] %>%
    cbind(years, .) %>%
    mutate(plot_id = unlist(filter_plot), trait_count = dim(trait_mat)[2])
    write_tsv(fd_out, paste0(here::here("data"), "/fd_output/", filter_plot, "_fd.tsv"))

@@

First pass at calculating FD metrics from FD package:
```{r}
data <- biotime_traits %>% 
  filter(!is.na(plot)) %>% #remove unlabeled plots 
  group_by(plot_id, year) %>%
  filter(n_distinct(id) > 4) %>%
  group_by(plot_id) %>%
  filter(n_distinct(year) > 4) %>% 
  ungroup() #%>%
  #filter(#!study_id %in% c(195, 360), #exclude because they break
         #!study_id %in% c(217, 327, 195)) #exclude to get the file size smaller
```

@@

remain <- data %>%
  filter(!plot_id %in% fd_data$plot_id)

plot_sizes <- remain %>%
  count(plot_id)

#get_fd_error <- safely(get_fd)
#system.time(fd <- map(plot_sizes$plot_id, get_fd_error, obs_data = data, corr = "cailliez"))
system.time(fd <- map(plot_sizes$plot_id, get_fd_safe, obs_data = data, corr = "cailliez"))
```

@@

usethis::use_data(fd_table)
pins::pin(fd_table, board = "github")
```
